---
title: "OPER 655 - Text Mining"
subtitle: "{enter text mining goal}: Concepts & Mathematical Foundations"
author: "{ enter group member names }"
date: '`r format(Sys.Date(), "%d %b %Y")`'
output: 
  slidy_presentation:
    smart: no
    fig_caption: yes
    footer: "{ enter text mining goal }: Concepts & Mathematical Foundations"
graphics: yes
---

# Introduction

```{css, echo=F}
div.plotly.html-widget {width: 800px;
                   height: 800px;
                   margin-left:auto;
                   margin-right:auto;}
```

```{r load_resources, echo=FALSE}
knitr::opts_chunk$set(echo = !FALSE, 
                      fig.align = 'center',
                      message = F,
                      comment = ">>>",
                      warning = F)

shiny::includeCSS("resources/css/flatly-style.css")
shiny::includeCSS("resources/css/r-title.css")
shiny::includeScript("resources/js/jquery.min.js")
shiny::includeScript("resources/js/jkf-scroll.js")
```

```{r load_packages, echo=FALSE}
## put library() calls here for R packages
library(knitr)

## reticulate creates a connection between R and Python
library(reticulate)


## shouldn't need to uncomment the line below
## but if you have trouble importing python libraries
## you can specify which version of Python to use
#-----------------------------------------------------
#reticulate::use_python("C:/Path/to/my/python.exe")
```

```{python load_libraries, echo=FALSE}
## import python libraries here
## Note that reticulate, by default, looks for 
## libraries in a python environment called r-reticulate
##
## also, you must run the previous chunk first to connect R to
## the r-reticulate environment
import pandas as pd
import numpy as np
```

## Two hashtags creates a new section on the same slide

-   Main level bullet content here

    -   second level bullet content here as an unordered list
    -   second level bullet content here as an unordered list
    -   second level bullet content here as an unordered list

-   Here's an R code chunk

```{r cars}
summary(cars)
```

```{python}
## convert r object `cars` to a python object
## R data.frame objects automatically converted to a 
## Python pandas DataFrame object  
py_cars = r.cars

type(py_cars)

py_cars.head()
```

## New Section on same slide

-   Main level bullet content here

    1.  second level bullet content here as an ordered list
    2.  second level bullet content here as an ordered list
    3.  second level bullet content here as an ordered list

# One hashtag creates a new slide

## Slides should begin with a section heading

-   Content on slide 2

```{r pressure, echo=FALSE, fig.cap="A figure caption"}
plot(pressure)
```
